### 2019-01-24 texs/paper_base.tex
implement for cuda

In this thesis, we applied seq-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.

@@

% 477 words.
LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the seq-to-seq (sequence to sequence) model.
SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.

Seq-to-seq model is composed of two modules, the encoder netwrok and the decoder network.

@@

% (TODO) BiLSTMとmulti-layerについてさらっと

\subsection{Attention}
Attention is a extension module of seq-to-seq model to improve the quality of translation. 
Simple seq-to-seq model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
regardless of the length of the input sequence $sx$. 
Therefore, the longer the length of the input becomes, the more likely the information of the input will be lost.
This problem is eased by using the information in the encoding network when decoding the output sequence.

The attention module is first developed in \cite{attention_paper}.
However, the attention 
We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
In this subsection, we will describe about the global general attention.

@@

\subsection{Seq-to-Tree}
% 184 words
Compare to natural languages, programming languages obeys rigid grammer, wich is usually context free grammer,  
and it is reasonable to consider the grammer of the programming language in generating programs.
Seq-to-Tree is a model for generating tree-structured output from sequence input. This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages. 
This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.

Now, we will describe about the seq-2-tree model.
seq-2-tree model is composed of two modules, the encoder netwrok and the decoder network.
The encoder network of seq-2-tree model is the same as the encoder network of seq-2-tree model. It summerize the input sequence into one fixed length vector.

The decoder network is a network for generating tree structured output. 
In this paper, our implemented model is based on model in \cite{Seq2Tree}. 
So first, we briefly describe the model implemented in the paper, and then, we describe our model.

\subsubsection{Previous Model}
% 312 words
In algorithmic parspective, the inference of the seq2seq model tries to generate sequence one by one, from the first token to the last.
% The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
The inference of the SeqTree model starts from the start symbol, and recursively expand the nonterminal symbols in depth-first order.

The tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
Suppose the tree $ty$ is generated by the action sequence $ [a_1, \dots a_m] $, 
where $ a_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [a_1, \dots a_{k-1}] $. 
Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
so the seq-2-seq model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.

@@

\subsubsection{Our Model}

Calculating context With 
We changed previous model

Our model tries to exploit the intuitive that each node of the tree is basically independent from its sibling.
This intuition is not true when the compiler optimizes the assembler. 
However, in this paper, we tested the

@@

\section{Model Configuration}
The training model was implemented with Chainer. Source codes are avaiable at \url{}.

@@

BLEU is

@@

We tested our methods for

>>>>

In this thesis, we applied sequence-to-tree model suggested in \cite{Seq2Tree}, because the input of the decompiler is the sequence of machine codes.

@@

% 477 words.
LSTM unit is applied for SMT task in \cite{seq2seq}, as the essential unit of the sequence-to-sequence (sequence to sequence) model.
SMT is the task which tries to translate one sentense $sx$ written in one language into the sentense $sy$ written in another language.

Sequence-to-sequence model is composed of two modules, the encoder netwrok and the decoder network.

@@

In addition to

First is the Bidirectional Reccurent Neural Networks (BRNN) is the architecture introduced in \cite{BiRNN}.
In the experiment, this architecture is used for the encoder network as follows.
In addition to the internal state $ enc_{k} $, the reverse internal state $ enc_{k}^{\gets} $ is also calculated 
in accordance with the recursive formula $ enc_{k}^{\gets} = lstm_{enc}^{\gets}(enc_{k+1}^{\gets},vx_{k}) $.
Then both of the internal states $ enc_{n} $ and $ enc_{1}^{\gets} $ are used for decoder network.

Second is the multi-layer reccurent neural networks, introduced in ここ決める.
It is reported that, instead of the output of the LSTM units to another LSTM units will improve the accuracy of the prediction.
This architecture is called as stucked reccurent neural networks or multi-layer reccurent neural networks.

\subsection{Attention}
Attention is a extension module of sequence-to-sequence model to improve the quality of translation. 
Simple sequence-to-sequence model has a problem that the length of the encoded vector $enc_{n}$ is fixed 
regardless of the length of the input sequence $sx$. 
Therefore, the longer the length of the input becomes, the more likely the information of the input will be lost.
This problem is eased by using the information in the encoding network when decoding the output sequence.

The attention module is first developed in \cite{attention_paper}.
We inplemented the global general attention, which is intoduced in \cite{dot_attention}, for improving the quality of decompilation.
In this subsection, we will describe about the global general attention.

In the pure sequence-to-sequence model, the conditional probability  $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $ is calculated from $ dec_{k} $ ,which is the internal state of the decoder network.
In the sequence-to-sequence with attention model, the probability is calcutated from $ dec_{k} $ and the context vevctor $ c_{k} $.
$ c_{k} $

@@

\subsection{Sequence-to-Tree}
% 184 words
Compare to natural languages, programming languages obeys rigid grammer, wich is usually context free grammer,  
and it is reasonable to consider the grammer of the programming language in generating programs.
Sequence-to-Tree is a model for generating tree-structured output from sequence input. This model is introduced in \cite{Seq2Tree} for generating programs from the program specification written in natural languages. 
This task is similer to our task, which aims to generate programs from the sequence of the assembly code, so we implemented this model in the experiment.

Now, we will describe about the sequence-2-tree model.
sequence-to-tree model is composed of two modules, the encoder netwrok and the decoder network.
The encoder network of sequence-2-tree model is the same as the encoder network of sequence-to-tree model. It summerize the input sequence into one fixed length vector.

The decoder network is a network for generating tree structured output. 
A tree-structure is representable by the sequence of the actions which expands a nonterminal symbol of the constructing tree.
Suppose the tree $ty$ is generated by the action sequence $ [a_1, \dots a_m] $, 
where $ a_k $ is the action which expands left-most symbol of the nonterminal symbol in the tree generated by the action sequence $ [a_1, \dots a_{k-1}] $. 
Then, the tree-generating probability $ p(ty|sx) $ is decomposed to $ \prod_{k=1}^n p(a_k|sx,[a_1, \dots a_{k-1}]) $, 
so the sequence-to-sequence model is now applicable for generating tree structure, by emmbeding each action to representing vector $av_k$ and 
calculating $ LSTM_{dec}(dec_{k},av_{k}) $ for estimating $p(a_{k+1}|sx,[a_1, \dots a_{k}]) $.

% In algorithmic parspective, the inference of the seq2seq model tries to generate sequence one by one, from the first token to the last.
% The Seq2Tree model also tries to generate tree structure one by one, with depth-first order.
% The inference of the SeqTree model starts from the start symbol, and recursively expand the nonterminal symbols in depth-first order.

@@

@@

\section{Model Configuration}
The training model was implemented with Chainer. 
We implemented three models, Seq2seq, Seq2seqWithAattention, and Seq2tree.

The encoding module was bidirectional LSTM in all of three models.
The decoding module of Seq2seq and Seq2seqWithAattention predict the conditional probability of a next token $ p(sy_k|sx,[sy_1,\dots,sy_{k-1}]) $.
The decoding module of Seq2tree predicts the conditional probability of a next action $ p(a_{k}|sx,[a_1, \dots a_{k-1}]) $.

Seq2seqWithAattention and Seq2tree have attention module, while Seq2seq have not.

\begin{figure}
	\begin{tabular}{c|c}
		Number of Layers & 4
		%Dimensionality of Embedded Vectors & 128
	\end{tabular}
	\caption{The configuration parameter of the models}
	\label{fig:parameterofmodels}
\end{figure}

Figure~\ref{fig:parameterofmodels} shows the parameter of the models.

@@

BLEU is the metrics for the naturallity of the generated program. 
It is first introduced in \cite{BLEU}, for evaluating the performance of the machine translation.

@@

We tested three models. 
Seq2seq is a model with
